%
% Distribution list file formatted for package 'mailing'
%
% Entry format:
% Name of addressee
% Address (use \\ for new line)
% Opening text of the letter
% <blank line>
%
%-------------------------------------------------------------------------------
% KTH Mekanik
%-------------------------------------------------------------------------------
%
Prof. Arne Johansson
KTH Mechanics\\100 44 Stockholm, Sweden
Dear Prof. Johansson,

Prof. Nicholas Apazidis
KTH Mechanics\\100 44 Stockholm, Sweden
Dear Prof. Apazidis,

Prof. Philipp Schlatter
KTH Mechanics\\100 44 Stockholm, Sweden
Dear Prof. Schlatter,

Prof. Dan Henningson
KTH Mechanics\\100 44 Stockholm, Sweden
Dear Prof. Henningson,

Dr. Anders Dahlkild
KTH Mechanics\\100 44 Stockholm, Sweden
Dear Dr. Dahlkild,

Dr. Hanno Essén
KTH Mechanics\\100 44 Stockholm, Sweden
Dear Dr. Essén,

Dr. Christophe Duwig
KTH Mechanics\\100 44 Stockholm, Sweden
Dear Dr. Duwig,

Dr. Antonio Segalini
KTH Mechanics\\100 44 Stockholm, Sweden
Dear Dr. Segalini,

Prof. Henrik Alfredsson
KTH Mechanics\\100 44 Stockholm, Sweden
Dear Prof. Alfredsson,

Prof. Luca Brandt
KTH Mechanics\\100 44 Stockholm, Sweden
Dear Prof. Brandt,

Dr. Outi Tammisola
KTH Mechanics\\100 44 Stockholm, Sweden
Dear Dr. Tammisola,

Prof. Fredrik Lundell,
KTH Mechanics\\100 44 Stockholm, Sweden
Dear Prof. Lundell,

% Pedro, Daulet, Sagar, Martin, Krishne, Santosh, Velibor, Anthony, Armin,
% Arash, Giandomenico, Prabal, Binbin, Marco, Mehdi, Ali, Nicolas, Emad,

%-------------------------------------------------------------------------------
% KTH
%-------------------------------------------------------------------------------
%

%-------------------------------------------------------------------------------
% Sweden
%-------------------------------------------------------------------------------
%

Department of Meteorology
Stockholm University\\106 91 Stockholm, Sweden
Dear Sir/Madam

Department of Earth Sciences
Geocentrum, Villavägen 16\\752 36 Uppsala, Sweden
Dear Sir/Madam

SMHI, Rossby Centre
601 76 Norrköping\\Sweden
Dear Sir/Madam

Prof. Gunilla Svensson
Meteorologiska institutionen (MISU)\\106 91 Stockholm, Sweden
Dear Prof. Svensson,

Prof. Rodrigo Caballero
Meteorologiska institutionen (MISU)\\106 91 Stockholm, Sweden
Dear Prof. Caballero,

Prof. Jonas Nycander
Meteorologiska institutionen (MISU)\\106 91 Stockholm, Sweden
Dear Prof. Nycander,

%-------------------------------------------------------------------------------
% Europe
%-------------------------------------------------------------------------------
%

Dr. Andrea Maffioli
LMFA, École Centrale de Lyon\\36, avenue Guy de Collongue\\69134 Écully cedex\\France
Dear Dr. Maffioli,

Dr. Jo\"el Sommeria
Laboratoire LEGI, CS 40700\\38058 Grenoble Cedex 9\\France
Dear Dr. Sommeria,

Dr. Pierre Augier
Laboratoire LEGI, CS 40700\\38058 Grenoble Cedex 9\\France
Dear Dr. Augier,

%-------------------------------------------------------------------------------
% World
%-------------------------------------------------------------------------------
%

Jibu Tom Jose
4006 Linkwood Rd Apt B\\Baltimore, MD 21210\\U.S.A.
Dear Jibu,

Parvathi Madathil Kooloth
1048 Cherry Blossom Dr\\Verona, WI 53593\\U.S.A.
Dear Parvathi,

Prof. Tapan K. Sengupta
Department of Aerospace Engg.\\IIT Kanpur\\Kanpur --- 208016\\India
Dear Prof. Sengupta,

Dr. Rakesh K. Mathpal
Department of Aerospace Engg.\\IIT Kanpur\\Kanpur --- 208016\\India
Dear Dr. Mathpal,

Dr. Alakesh C. Mandal
Department of Aerospace Engg.\\IIT Kanpur\\Kanpur --- 208016\\India
Dear Dr. Mandal,

Dr. Sudhakar Yogaraj
Department of Mechanical Sciences\\IIT Goa\\Farmagudi, Goa -- 403401\\India
Dear Dr. Yogaraj,

Dr. Ganesh Tamadapu
Department of Applied Mechanics\\Indian Institute of Technology Madras\\Chennai -- 600 036\\INDIA
Dear Dr. Tamadapu,

Prof. Prabhu Ramachandran
Department of Aerospace Engg.\\IIT Bombay, Mumbai --- 400 076\\India
Dear Prof. Ramachandran,

Dr. Rama Govindarajan
ICTS\\Hesaraghatta Hobli\\Bengaluru --- 560 089\\India
Dear Dr. Govindarajan,

Dr. Jeffrey S. Oishi
Carnegie Science Room 141\\Bates College\\Lewiston, ME 04240\\U.S.A.
Dear Dr. Oishi,

Dr. Daniel Lecoanet
415 Jadwin Hall\\
Dear Dr. Lecoanet,

Dr. Keaton J. Burns
Flatiron Institute\\162 Fifth Avenue, 4th Floor\\New York, NY 10010\\U.S.A.
Dear Dr. Burns,

Dr. Jim Thomas,
Clark 224, Mail Stop: 29\\266 Woods Hole Road\\Woods Hole, MA 02543-1050\\U.S.A.
Dear Dr. Thomas,

Dr. Mikael Mortensen
Postboks 1053\\Blindern\\0316 Oslo\\Norway
Dear Dr. Mortensen,

Prof. Peter Bartello
Burnside Hall 910\\805 Sherbrooke Street West\\Montreal, Quebec H3A 0B9\\Canada
Dear Prof. Bartello,

%-------------------------------------------------------------------------------
% Committee
%-------------------------------------------------------------------------------
%

Dr. Clara Marika Velte
DTU, Nils Koppels Allé\\Building 403, Room 106\\2800 Kgs. Lyngby, Denmark
Dear Dr. Velte,

Prof. Johan Nilsson
Meteorologiska institutionen (MISU)\\106 91 Stockholm, Sweden
Dear Prof. Nilsson,

Dr. Thorsten Mauritsen
Meteorologiska institutionen (MISU)\\106 91 Stockholm, Sweden
Dear Dr. Mauritsen,

Prof. James J. Riley
University of Washington\\Mechanical Engineering Building, Room 314\\Seattle, WA 98195, U.S.A.
Dear Prof. Riley


% Leave a blank line at the end of the list

